---
title: "Milestone 3"
author: "Daniel Shapiro"
date: "2/19/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# I made echo = TRUE because I want for Preceptor to be able to see my code comments.

library(foreign)
library(plyr)
library(dplyr)
library(Hmisc)
library(arm)
library(stargazer)
library(ggthemes)

require(ggplot2)
require(reshape2)
require(devtools)
require(scales)
library(lme4)

library(magrittr)
library(ggthemes)
library(RColorBrewer)

library(multiwayvcov)
library(sandwich)
library(lmtest)
library(ggplot2)
library(interactions)
```

### Data Management

```{r}
data <- read.csv2("raw-data/wp_data_raw.csv")
stargazer(data)
```

## Function 

```{r}
recode_dummy <- function(.df, 
                         .name_q,
                         .val) {
  return(ifelse(test = (.df[,.name_q] != .val | is.na(.df[, .name_q])), 
                yes = 0, 
                no = 1))
}

data$V1RL <- recode_dummy(.df = data, 
                          .name_q = "Q1", 
                          .val = 1)
varnames <- paste0("Q", c(1,3,5,seq(8,22,2)))


## Loop for RL

for (i in 1:10) {
  .name_dummy <- paste0("V",i,"RL")
  data[,.name_dummy] <- recode_dummy(.df = data, 
                                     .name_q = varnames[i], 
                                     .val = 1)
}


## Loop for Sharia 

for (i in 1:10) {
  .name_dummy <- paste0("V",i,"S")
  data[,.name_dummy] <- recode_dummy(.df = data, 
                                     .name_q = varnames[i], 
                                     .val = 2)
}


## Loop for Adat 

for (i in 1:10) {
  .name_dummy <- paste0("V",i,"A")
  data[,.name_dummy] <- recode_dummy(.df = data, 
                                     .name_q = varnames[i], 
                                     .val = 3)
}



##### INDEX for preference for Russian Law

data$indexRL<-NA
data$indexRL <- (data$V1RL + data$V2RL + data$V3RL + data$V4RL + data$V5RL +
                   data$V6RL + data$V7RL + data$V8RL + data$V9RL + data$V10RL)/10

hist(data$indexRL)

##### INDEX for preference for Sharia

data$indexS<-NA
data$indexS <- (data$V1S + data$V2S + data$V3S + data$V4S + data$V5S +
                  data$V6S + data$V7S + data$V8S + data$V9S + data$V10S)/10
hist(data$indexS)

##### INDEX for preference for Adat

data$indexA<-NA
data$indexA <- (data$V1A + data$V2A + data$V3A + data$V4A + data$V5A +
                  data$V6A + data$V7A + data$V8A + data$V9A + data$V10A)/10
hist(data$indexA)
```

## Covariates 

## Age Cohorts

```{r}
data$age_cohorts <- NA
data$age_cohorts[data$age > 17 & data$age < 30]<- "youth"
data$age_cohorts[data$age > 29 & data$age < 50]= "midage"
data$age_cohorts[data$age > 49 & data$age < 83]= "older"
```

## Imputation 

```{r}
library(mi)
library(Hmisc)
```

## Education 

```{r}
x<-cbind(data$edu,data$female,data$age,data$urban, data$urban_Soviet, data$knowRL, data$unemployed)
datax<-as.data.frame(x)
mdf<-missing_data.frame(datax)
imp.mi<-mi(mdf)
newdata<-complete(imp.mi,m=1)

data$edufull<-newdata$V1
```

## Income 

```{r}
x<-cbind(data$income, data$edufull, data$female, data$age,data$urban, data$official, data$unemployed)
datax<-as.data.frame(x)
mdf<-missing_data.frame(datax)
imp.mi<-mi(mdf)
newdata<-complete(imp.mi,m=1)

data$incomefull<-newdata$V1

write.csv2(data, file = "wp_data_survey.csv")
```


############## Analysis #####################

```{r}
data <- read.csv2("raw-data/wp_data_survey.csv")
```

## Table1

```{r}
m1 <- lm(indexRL ~ killed + wounded + damaged + displaced + female + 
           as.factor(age_cohorts) + incomefull + edufull + unemployed + urban_com, data=data) 
summary(m1) 

m2 <- lm(indexS ~ killed + wounded + damaged + displaced + female + 
           as.factor(age_cohorts) + incomefull + edufull + unemployed + urban_com, data=data) 
summary(m2) 

m3 <- lm(indexA ~ killed + wounded + damaged + displaced + female + 
           as.factor(age_cohorts) + incomefull + edufull + unemployed + urban_com, data=data) 
summary(m3) 
stargazer(m1, m2, m3, title="OLS Regression Analysis of the Impact of Victimization on Legal Preferences", align=TRUE, no.space=TRUE)

stargazer(m1, m2, m3, title="OLS Regression Analysis of the Impact of Victimization on Legal Preferences", align=TRUE, no.space=TRUE,
          type="html",
          out="table1.doc")
```

## Table 2

```{r}
m1 <- lm(indexRL ~ com_exposure*female + 
           as.factor(age_cohorts) + incomefull + edufull + unemployed + urban_com + 
           russ_pop + lmaltitude + ldistance_Grozny + lcom_size + as.factor(rayon), data = data)
summary(m1)

m1_vcov <- cluster.vcov(m1, data$location)

coeftest(m1, vcov. = m1_vcov)

cluster_se <- sqrt(diag(cluster.vcov(m1, data$location)))

m2 <- lm(indexS ~ com_exposure*female + 
           as.factor(age_cohorts) + incomefull + edufull + unemployed + urban_com + 
           russ_pop + lmaltitude + ldistance_Grozny + lcom_size + as.factor(rayon), data = data)
summary(m2)

m2_vcov <- cluster.vcov(m2, data$location)

coeftest(m2, vcov. = m2_vcov)

cluster_se <- sqrt(diag(cluster.vcov(m2, data$location)))


m3 <- lm(indexA ~ com_exposure*female + 
           as.factor(age_cohorts) + incomefull + edufull + unemployed + urban_com + 
           russ_pop + lmaltitude + ldistance_Grozny + lcom_size + as.factor(rayon), data = data)
summary(m3)

m3_vcov <- cluster.vcov(m3, data$location)

coeftest(m3, vcov. = m3_vcov)

cluster_se <- sqrt(diag(cluster.vcov(m2, data$location)))

stargazer(m1, m2, m3, se = list(coeftest(m1, vcov. = m1_vcov)[,2],
                                coeftest(m2, vcov. = m2_vcov)[,2],
                                coeftest(m3, vcov. = m3_vcov)[,2]),
          type="html",
          out="table2.doc")
```

## Predicted Values 

```{r}
m1 <- lm(indexRL ~ com_exposure*female + 
  as.factor(age_cohorts) + incomefull + edufull + unemployed + urban_com +
    russ_pop + lmaltitude + ldistance_Grozny + lcom_size, data = data)
summary(m1)

newdata1 = data.frame(com_exposure = 0, female = 0, age_cohorts = 'midage',
                      incomefull = mean(data$incomefull), edufull = mean(data$edufull),
                      unemployed = 0, urban_com = 1, russ_pop = mean(data$russ_pop), 
                      lmaltitude = mean(data$lmaltitude), ldistance_Grozny = mean(data$ldistance_Grozny),
                      lcom_size = mean(data$lcom_size))

newdata2 = data.frame(com_exposure = 0, female = 1, age_cohorts = 'midage',
                      incomefull = mean(data$incomefull), edufull = mean(data$edufull),
                      unemployed = 0, urban_com = 1, russ_pop = mean(data$russ_pop), 
                      lmaltitude = mean(data$lmaltitude), ldistance_Grozny = mean(data$ldistance_Grozny),
                      lcom_size = mean(data$lcom_size))

newdata3 = data.frame(com_exposure = 1, female = 0, age_cohorts = 'midage',
                      incomefull = mean(data$incomefull), edufull = mean(data$edufull),
                      unemployed = 0, urban_com = 1, russ_pop = mean(data$russ_pop), 
                      lmaltitude = mean(data$lmaltitude), ldistance_Grozny = mean(data$ldistance_Grozny),
                      lcom_size = mean(data$lcom_size))

newdata4 = data.frame(com_exposure = 1, female = 1, age_cohorts = 'midage',
                      incomefull = mean(data$incomefull), edufull = mean(data$edufull),
                      unemployed = 0, urban_com = 1, russ_pop = mean(data$russ_pop), 
                      lmaltitude = mean(data$lmaltitude), ldistance_Grozny = mean(data$ldistance_Grozny),
                      lcom_size = mean(data$lcom_size))


newdata5 = data.frame(com_exposure = 0, female = 0, age_cohorts = 'midage',
                      incomefull = mean(data$incomefull), edufull = mean(data$edufull),
                      unemployed = 0, urban_com = 0, russ_pop = mean(data$russ_pop), 
                      lmaltitude = mean(data$lmaltitude), ldistance_Grozny = mean(data$ldistance_Grozny),
                      lcom_size = mean(data$lcom_size))

newdata6 = data.frame(com_exposure = 0, female = 1, age_cohorts = 'midage',
                      incomefull = mean(data$incomefull), edufull = mean(data$edufull),
                      unemployed = 0, urban_com = 0, russ_pop = mean(data$russ_pop), 
                      lmaltitude = mean(data$lmaltitude), ldistance_Grozny = mean(data$ldistance_Grozny),
                      lcom_size = mean(data$lcom_size))

newdata7 = data.frame(com_exposure = 1, female = 0, age_cohorts = 'midage',
                      incomefull = mean(data$incomefull), edufull = mean(data$edufull),
                      unemployed = 0, urban_com = 0, russ_pop = mean(data$russ_pop), 
                      lmaltitude = mean(data$lmaltitude), ldistance_Grozny = mean(data$ldistance_Grozny),
                      lcom_size = mean(data$lcom_size))

newdata8 = data.frame(com_exposure = 1, female = 1, age_cohorts = 'midage',
                      incomefull = mean(data$incomefull), edufull = mean(data$edufull),
                      unemployed = 0, urban_com = 0, russ_pop = mean(data$russ_pop), 
                      lmaltitude = mean(data$lmaltitude), ldistance_Grozny = mean(data$ldistance_Grozny),
                      lcom_size = mean(data$lcom_size))

predict(m1, newdata1, type = "response")
predict(m1, newdata2, type = "response")
predict(m1, newdata3, type = "response")
predict(m1, newdata4, type = "response")


predict(m1, newdata5, type = "response")
predict(m1, newdata6, type = "response")
predict(m1, newdata7, type = "response")
predict(m1, newdata8, type = "response")
```

########## Table 3

```{r}
data <- read.csv2("raw-data/wp_data_courts.csv")

## Last names of plaintiffs are reducted from these data for privacy reasons 

famdata <- data[which(data$family==1),]
nonfamdata <- data[which(data$family==0),]

m1 <- glm(istez_females ~ com_exposure + urban +
            mountainous + russ_pop + pop_fem_share + 
            as.factor(year),family=binomial(link='logit'),data=data)
summary(m1)

m1_vcov <- cluster.vcov(m1, data$uchastok)

coeftest(m1, vcov. = m1_vcov)

cluster_se <- sqrt(diag(cluster.vcov(m1, data$uchastok)))

stargazer(m1, se = list(coeftest(m1, vcov. = m1_vcov)[,2]), 
          omit.stat = c("rsq", "f", "adj.rsq", "ser"))

m2 <- glm(istez_females ~ com_exposure + urban +
            mountainous + russ_pop + pop_fem_share + 
            as.factor(year),family=binomial(link='logit'),data=famdata)
summary(m2)

m2_vcov <- cluster.vcov(m2, famdata$uchastok)

coeftest(m2, vcov. = m2_vcov)

cluster_se <- sqrt(diag(cluster.vcov(m2, famdata$uchastok)))

m3 <- glm(istez_females ~ com_exposure + urban +
            mountainous + russ_pop + pop_fem_share + 
            as.factor(year),family=binomial(link='logit'),data=nonfamdata)
summary(m3)

m3_vcov <- cluster.vcov(m3, nonfamdata$uchastok)

coeftest(m3, vcov. = m3_vcov)

cluster_se <- sqrt(diag(cluster.vcov(m3, nonfamdata$uchastok)))

stargazer(m1, m2, m3, se = list(coeftest(m1, vcov. = m1_vcov)[,2],
                                coeftest(m2, vcov. = m2_vcov)[,2],
                                coeftest(m3, vcov. = m3_vcov)[,2]))


stargazer(m1, m2, m3, se = list(coeftest(m1, vcov. = m1_vcov)[,2],
                                coeftest(m2, vcov. = m2_vcov)[,2],
                                coeftest(m3, vcov. = m3_vcov)[,2]),
          type="html",
          out="table3.doc")
```

## Predicted Probability 

```{r}
m1 <- glm(istez_females ~ com_exposure + urban + mountainous + russ_pop + pop_fem_share + family + as.factor(year),family=binomial(link='logit'),data=data)
summary(m1)

newdata1 = data.frame(com_exposure = 0, urban = 0, mountainous =0, russ_pop = 0, pop_fem_share = 0.5, family = 1, year = 2013)
newdata2 = data.frame(com_exposure = 1, urban = 0, mountainous =0, russ_pop = 0, pop_fem_share = 0.5, family = 1, year = 2013)

predict(m1, newdata1, type = "response")
predict(m1, newdata2, type = "response")

newdata3 = data.frame(com_exposure = 0, urban = 0, mountainous =1, russ_pop = 0, pop_fem_share = 0.5, family = 1, year = 2013)
newdata4 = data.frame(com_exposure = 1, urban = 0, mountainous =1, russ_pop = 0, pop_fem_share = 0.5, family = 1, year = 2013)

predict(m1, newdata3, type = "response")
predict(m1, newdata4, type = "response")

newdata5 = data.frame(com_exposure = 0, urban = 1, mountainous =0, russ_pop = 0, pop_fem_share = 0.5, family = 1, year = 2013)
newdata6 = data.frame(com_exposure = 1, urban = 1, mountainous =0, russ_pop = 0, pop_fem_share = 0.5, family = 1, year = 2013)

predict(m1, newdata5, type = "response")
predict(m1, newdata6, type = "response")

newdata7 = data.frame(com_exposure = 0, urban = 0, mountainous =0, russ_pop = 0, pop_fem_share = 0.5, family = 0, year = 2013)
newdata8 = data.frame(com_exposure = 1, urban = 0, mountainous =0, russ_pop = 0, pop_fem_share = 0.5, family = 0, year = 2013)

predict(m1, newdata7, type = "response")
predict(m1, newdata8, type = "response")
```

#################################### FIGURES

```{r}
data <- read.csv2("raw-data/wp_data_raw.csv")
```

##### Figure 2

### Intergating 

```{r}
# This code was originally here, but the link threw an Error 404, so I'm just putting it in the comments. suppressMessages("https://raw.github.com/gerasy1987/useful_r/master/functions.R" %>% devtools::source_url()). My guess is that this was simply used to make sure that the code ran smoother.

multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {
  library(grid)
  
  # Make a list from the ... arguments and plotlist
  plots <- c(list(...), plotlist)
  
  numPlots = length(plots)
  
  # If layout is NULL, then use 'cols' to determine layout
  if (is.null(layout)) {
    # Make the panel
    # ncol: Number of columns of plots
    # nrow: Number of rows needed, calculated from # of cols
    layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
                     ncol = cols, nrow = ceiling(numPlots/cols))
  }
  
  if (numPlots==1) {
    print(plots[[1]])
    
  } else {
    # Set up the page
    grid.newpage()
    pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))
    
    # Make each plot, in the correct location
    for (i in 1:numPlots) {
      # Get the i,j matrix positions of the regions that contain this subplot
      matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))
      
      print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
                                      layout.pos.col = matchidx$col))
    }
  }
}
```

### Plot 1.1: Child Custody Forum

```{r}
h1 <- ggplot(data=data[!is.na(data$Q1),], 
             aes(factor(Q1))) + 
  geom_bar(aes(y = (..count..)/sum(..count..)),
           fill=("grey69"), position = "dodge") + 
  geom_text(aes(y = ((..count..)/sum(..count..)), 
                label = round((..count..)/sum(..count..), digits = 2)), 
            stat = "count", vjust = -0.25, size = 8) +
  scale_y_continuous(limits=c(0, .8)) +
  scale_x_discrete(labels=c("1" = "State Law","2" = "Sharia","3" = "Adat", "4" = "Don't Know")) +
  labs(title = "Child Custody",
       y = "Share",
       x = "") +
  theme_few(base_size = 20, base_family = "Helvetica")
```

### Plot 2.1: Domestic Violence 

```{r}
h2 <- ggplot(data=data[!is.na(data$Q3_graph),], 
             aes(factor(Q3_graph))) + 
  geom_bar(aes(y = (..count..)/sum(..count..)),
           fill=("grey69"), position = "dodge") + 
  geom_text(aes(y = ((..count..)/sum(..count..)), 
                label = round((..count..)/sum(..count..), digits = 2)), 
            stat = "count", vjust = -0.25, size = 8) +
  scale_y_continuous(limits=c(0, .8)) +
  scale_x_discrete(labels=c("1" = "State Law","2" = "Sharia","3" = "Adat", "4" = "Don't Know")) +
  labs(title = "Domestic Violence",
       y = "Share",
       x = "") +
  theme_few(base_size = 20, base_family = "Helvetica")
```

### Plot 3.1: Bride Kidnapping

```{r}
h3 <- ggplot(data=data[!is.na(data$Q5_graph),], 
             aes(factor(Q5_graph))) + 
  geom_bar(aes(y = (..count..)/sum(..count..)),
           fill=("grey69"), position = "dodge") + 
  geom_text(aes(y = ((..count..)/sum(..count..)), 
                label = round((..count..)/sum(..count..), digits = 2)), 
            stat = "count", vjust = -0.25, size = 8) +
  scale_y_continuous(limits=c(0, .8)) +
  scale_x_discrete(labels=c("1" = "State Law","2" = "Sharia","3" = "Adat", "4" = "Don't Know")) +
  labs(title = "Bride Kidnapping",
       y = "Share",
       x = "") +
  theme_few(base_size = 20, base_family = "Helvetica")
```

### Plot 4.1: Honor Killing


```{r}
h4 <- ggplot(data=data[!is.na(data$Q8_graph),], 
             aes(factor(Q8_graph))) + 
  geom_bar(aes(y = (..count..)/sum(..count..)),
           fill=("grey69"), position = "dodge") + 
  geom_text(aes(y = ((..count..)/sum(..count..)), 
                label = round((..count..)/sum(..count..), digits = 2)), 
            stat = "count", vjust = -0.25, size = 8) +
  scale_y_continuous(limits=c(0, .8)) +
  scale_x_discrete(labels=c("1" = "State Law","2" = "Sharia","3" = "Adat", "4" = "Don't Know")) +
  labs(title = "Honor Killing",
       y = "Share",
       x = "") +
  theme_few(base_size = 20, base_family = "Helvetica")
```

### Plot 5.1: Polygamy

```{r}
h5 <- ggplot(data=data[!is.na(data$Q10),], 
             aes(factor(Q10))) + 
  geom_bar(aes(y = (..count..)/sum(..count..)),
           fill=("grey69"), position = "dodge") + 
  geom_text(aes(y = ((..count..)/sum(..count..)), 
                label = round((..count..)/sum(..count..), digits = 2)), 
            stat = "count", vjust = -0.25, size = 8) +
  scale_y_continuous(limits=c(0, .8)) +
  scale_x_discrete(labels=c("1" = "State Law","2" = "Sharia","3" = "Adat", "4" = "Don't Know")) +
  labs(title = "Polygamy",
       y = "Share",
       x = "") +
  theme_few(base_size = 20, base_family = "Helvetica")
```


### Plot 6.1: Inheritance 

```{r}
table(data$Q12)

h6 <- ggplot(data=data[!is.na(data$Q12),], 
             aes(factor(Q12))) + 
  geom_bar(aes(y = (..count..)/sum(..count..)),
           fill=("grey69"), position = "dodge") + 
  geom_text(aes(y = ((..count..)/sum(..count..)), 
                label = round((..count..)/sum(..count..), digits = 2)), 
            stat = "count", vjust = -0.25, size = 8) +
  scale_y_continuous(limits=c(0, .8)) +
  scale_x_discrete(labels=c("1" = "State Law","2" = "Sharia","3" = "Adat", "4" = "Don't Know")) +
  labs(title = "Inheritance",
       y = "Share",
       x = "") +
  theme_few(base_size = 20, base_family = "Helvetica")
```

### Plot 7.1: Property 

```{r}
table(data$Q14)

h7 <- ggplot(data=data[!is.na(data$Q14),], 
             aes(factor(Q14))) + 
  geom_bar(aes(y = (..count..)/sum(..count..)),
           fill=("grey69"), position = "dodge") + 
  geom_text(aes(y = ((..count..)/sum(..count..)), 
                label = round((..count..)/sum(..count..), digits = 2)), 
            stat = "count", vjust = -0.25, size = 8) +
  scale_y_continuous(limits=c(0, .8)) +
  scale_x_discrete(labels=c("1" = "State Law","2" = "Sharia","3" = "Adat", "4" = "Don't Know")) +
  labs(title = "Property",
       y = "Share",
       x = "") +
  theme_few(base_size = 20, base_family = "Helvetica")

```

### Plot 8.1: Car Incident  

```{r}
table(data$Q16)

h8 <- ggplot(data=data[!is.na(data$Q16),], 
             aes(factor(Q16))) + 
  geom_bar(aes(y = (..count..)/sum(..count..)),
           fill=("grey69"), position = "dodge") + 
  geom_text(aes(y = ((..count..)/sum(..count..)), 
                label = round((..count..)/sum(..count..), digits = 2)), 
            stat = "count", vjust = -0.25, size = 8) +
  scale_y_continuous(limits=c(0, .8)) +
  scale_x_discrete(labels=c("1" = "State Law","2" = "Sharia","3" = "Adat", "4" = "Don't Know")) +
  labs(title = "Car Accident",
       y = "Share",
       x = "") +
  theme_few(base_size = 20, base_family = "Helvetica")
```

### Plot 9.1: Debt

```{r}
table(data$Q18)

h9 <- ggplot(data=data[!is.na(data$Q18),], 
             aes(factor(Q18))) + 
  geom_bar(aes(y = (..count..)/sum(..count..)),
           fill=("grey69"), position = "dodge") + 
  geom_text(aes(y = ((..count..)/sum(..count..)), 
                label = round((..count..)/sum(..count..), digits = 2)), 
            stat = "count", vjust = -0.25, size = 8) +
  scale_y_continuous(limits=c(0, .8)) +
  scale_x_discrete(labels=c("1" = "State Law","2" = "Sharia","3" = "Adat", "4" = "Don't Know")) +
  labs(title = "Debt",
       y = "Share",
       x = "") +
  theme_few(base_size = 20, base_family = "Helvetica")
```

### Plot 10.1: Murder

```{r murder}
table(data$Q20)

h10 <- ggplot(data=data[!is.na(data$Q20),], 
              aes(factor(Q20))) + 
  geom_bar(aes(y = (..count..)/sum(..count..)),
           fill=("grey69"), position = "dodge") + 
  geom_text(aes(y = ((..count..)/sum(..count..)), 
                label = round((..count..)/sum(..count..), digits = 2)), 
            stat = "count", vjust = -0.25, size = 8) +
  scale_y_continuous(limits=c(0, .8)) +
  scale_x_discrete(labels=c("1" = "State Law","2" = "Sharia","3" = "Adat", "4" = "Don't Know")) +
  labs(title = "Murder",
       y = "Share",
       x = "") +
  theme_few(base_size = 20, base_family = "Helvetica")


figure2 <- multiplot(h1, h2, h3, h4, h5, h6, h7, h8, h9, h10, cols = 2)
```

## Figure 3
```{r}
data <- read.csv2("raw-data/wp_data_survey.csv")
range01 <- function(x) {(x - min(x))/(max(x) - min(x))}
require(plyr)
length2 <- function (x, na.rm=FALSE) {
  if (na.rm) sum(!is.na(x))
  else       length(x)
}

if (!require(pacman)) install.packages("pacman")
pacman::p_load(readr, ggplot2, plyr, dplyr, magrittr, tidyr, purrr, ggthemes)

means1 <- round(tapply(data$indexRL, data$female, mean, na.rm = T), digits=3)
sds1 <- round(tapply(data$indexRL, data$female, sd, na.rm = T), digits=3)
n1 <- tapply(data$indexRL, data$female, length2, na.rm = T)
se1 <- round(sds1/sqrt(n1), digits=3)
error1 <- round((qt(0.975,df=n1-1)*se1), digits = 3)
min <- c(0,1)
object1 <- c(1,1)

means2 <- round(tapply(data$indexS, data$female, mean, na.rm = T), digits=3)
sds2 <- round(tapply(data$indexS, data$female, sd, na.rm = T), digits=3)
n2 <- tapply(data$indexS, data$female, length2, na.rm = T)
se2 <- round(sds2/sqrt(n2), digits=3)
error2 <- round((qt(0.975,df=n2-1)*se2), digits = 3)
object2 <- c(2,2)

means3 <- round(tapply(data$indexA, data$female, mean, na.rm = T), digits=3)
sds3 <- round(tapply(data$indexA, data$female, sd, na.rm = T), digits=3)
n3 <- tapply(data$indexA, data$female, length2, na.rm = T)
se3 <- round(sds3/sqrt(n3), digits=3)
error3 <- round((qt(0.975,df=n3-1)*se3), digits = 3)
object3 <- c(3,3)

V1_dat <- rbind(cbind(object1, min, means1, sds1, n1, se1, error1, deparse.level=0),
                cbind(object2, min, means2, sds2, n2, se2, error2, deparse.level=0),
                cbind(object3, min, means3, sds3, n3, se3, error3, deparse.level=0))

rownames(V1_dat) <- c(1:6) 
colnames(V1_dat) <- c("sum", "min", "put", "sds", "n", "se", "error") 
sb <- as.data.frame(V1_dat)


sb2 <- sb
sb2$min <- as.factor(sb2$min) 
sb2$sum <- as.factor(sb2$sum)
levels(sb2$sum) <- c("State Law", "Sharia", "Adat") 

figure3 <- ggplot(sb2, aes(x=sum, y=put, fill = min)) + 
  geom_bar(position=position_dodge(), 
           stat="identity", size=.3) +      
  geom_errorbar(aes(ymin=put-error, ymax=put+error),
                size=.5,    # Thinner lines
                width=.3,
                position=position_dodge(.9)) +
  xlab("") +
  ylab("") +
  ggtitle("") +
  coord_cartesian(ylim=c(0, .5))+  
  scale_y_continuous(breaks=seq(0, 0.5, .1)) +
  scale_fill_manual(name="Gender", # Legend label, use darker colors
                    # breaks=c("1", "2", "3"),
                    breaks=c("0", "1"), 
                    labels=c("male", 
                             "female"),
                    values=c("cornsilk3", "gray33")) +
  theme(text = element_text(size=25),
        axis.line = element_line(colour = "black"),
        axis.title.x = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank())
```

#### Figure 5

```{r}
data <- read.csv2("raw-data/wp_data_survey.csv")


data$victimized[data$com_exposure=='0']<-'nonvictimized'
data$victimized[data$com_exposure=='1']<-'victimized'

data$gender[data$female=='0']<-'male'
data$gender[data$female=='1']<-'female'

m1 <- lm(indexRL ~ victimized*gender + 
           as.factor(age_cohorts) + incomefull + edufull + unemployed + urban_com +
           russ_pop + lmaltitude + ldistance_Grozny + lcom_size, data = data)
summary(m1)

figure5 <- cat_plot(m1, pred = victimized, modx = gender, geom = "bar") + 
  labs(x="", y = "") +
  scale_color_manual("gender", values=c('grey20','grey60'))+
  scale_fill_manual("gender",values=c('grey30','grey80')) +
  theme_few(base_size = 20, base_family = "Helvetica")
  
```          

##### Figure 6

```{r}

total <- read.csv2("raw-data/wp_data_Chechnya_Ingushetia.csv")

ftotal <- total[which(total$data.female==1),]
mtotal <- total[which(total$data.female==0),]

means1 <- round(tapply(ftotal$data.indexRL, ftotal$chechnya, mean, na.rm = T), digits=3)
sds1 <- round(tapply(ftotal$data.indexRL, ftotal$chechnya, sd, na.rm = T), digits=3)
n1 <- tapply(ftotal$data.indexRL, ftotal$chechnya, length2, na.rm = T)
se1 <- round(sds1/sqrt(n1), digits=3)
error1 <- round((qt(0.975,df=n1-1)*se1), digits = 3)
min <- c(0,1)
object1 <- c(1,1)

means2 <- round(tapply(mtotal$data.indexRL, mtotal$chechnya, mean, na.rm = T), digits=3)
sds2 <- round(tapply(mtotal$data.indexRL, mtotal$chechnya, sd, na.rm = T), digits=3)
n2 <- tapply(mtotal$data.indexRL, mtotal$chechnya, length2, na.rm = T)
se2 <- round(sds2/sqrt(n2), digits=3)
error2 <- round((qt(0.975,df=n2-1)*se2), digits = 3)
min <- c(0,1)
object2 <- c(2,2)

V1_dat <- rbind(cbind(object1, min, means1, sds1, n1, se1, error1, deparse.level=0),
                cbind(object2, min, means2, sds2, n2, se2, error2, deparse.level=0))

rownames(V1_dat) <- c(1:4) 
colnames(V1_dat) <- c("sum", "min", "put", "sds", "n", "se", "error") 
sb <- as.data.frame(V1_dat)

sb2 <- sb
sb2$min <- as.factor(sb2$min) 
sb2$sum <- as.factor(sb2$sum)
levels(sb2$sum) <- c("Women", "Men") 

figure6 <- ggplot(sb2, aes(x=sum, y=put, fill = min)) + 
  geom_bar(position=position_dodge(), 
           stat="identity", size=.3) +      
  geom_errorbar(aes(ymin=put-error, ymax=put+error),
                size=.5,    # Thinner lines
                width=.3,
                position=position_dodge(.9)) +
  xlab("") +
  ylab("") +
  ggtitle("") +
  coord_cartesian(ylim=c(0, .5))+  
  scale_y_continuous(breaks=seq(0, 0.5, .1)) +
  scale_fill_manual(name="Region", # Legend label, use darker colors
                    # breaks=c("1", "2", "3"),
                    breaks=c("0", "1"), 
                    labels=c("Ingushetia", 
                             "Chechnya"),
                    values=c("gray88", "grey44")) +
  theme(text = element_text(size=25),
        axis.line = element_line(colour = "black"),
        axis.title.x = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank())
```