---
title: "Milestone 7"
author: "Daniel Shapiro"
date: "4/16/2020"
output: pdf_document
bibliography: bib.bib
link_citations: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(stargazer)
library(rstanarm)
library(bookdown)
library(foreign)
library(plyr)
library(dplyr)
library(Hmisc)
library(arm)
library(stargazer)
library(ggthemes)
require(ggplot2)
require(reshape2)
require(devtools)
require(scales)
library(lme4)
library(magrittr)
library(ggthemes)
library(RColorBrewer)
library(multiwayvcov)
library(sandwich)
library(lmtest)
library(ggplot2)
library(interactions)
library(tidybayes)
library(gt)
library(ggpubr)
```

# Abstract

Lazarev (2019) uses data describing individuals' choice between Russian state law, sharia law and customary law (adat) in Chechnya to show that gender can play a large role in societal splits in post-conflict societies. I was able to replicate all of the author's results. In my extension to Lazarev's paper, used the rstanarm package in R to check Lazarev's analysis with Bayesian regression, and the results confirmed the author's findings. I also pointed out certain areas where I disagreed somewhat with Lazarev's analysis and where I felt that the paper could improve. This paper's successful replication of Lazarev's findings helps strengthen Lazarev's argument about the role of gender in choice of legal organ, and my additional comments on Lazarev's anaylsis help to further discussion about postwar Chechnya and post-conflict society as a whole.

# Paper Overview and Introduction

This paper [@paper] by Egor Lazarev entitled "Laws In Conflict: Legacies of War, Gender, and Legal Pluralism in Chechnya" examines post-war Chechnya and how legacies of war affect people's choice between various legal processes. In modern-day Chechnya, there are three competing legal bodies: official Russian law, sharia courts [@sharia], and customary law (adat) [@adat]. The author argues that sharia and adat courts are traditionally more discriminatory towards women, and that women are more likely than men to turn to state courts rather than sharia courts or adat. The pattern of women choosing to turn to state courts for legal disputes rather than sharia or customary courts is exacerbated, as the author works to show through data, by the level to which a region was affected by violence during the Chechen wars [@wars]. In other words, conflict provided women with more opportunity to pursue their interests through official law. The author backs up his claim through data and through a comparison with neighboring Ingushetia, which has many similarities but has not gone through conflict. The enhanced opportunities for women in the legal process has been counterbalanced by an effort by the Ramzan Kadyrov government in Chechnya to retraditionalize the republic [@retraditionalize], and while women continue to look to state courts for assistance, Kadyrov works toward supporting more traditional forms of conflict resolution that favor men and Chechnya's traditionally patriarchal society. The author concludes that gender can play a large role in forming splits in post-conflict societies. Lazarev uses data throughout his paper to support his claims. The primary method he uses is ordinary least squares regression, in which Lazarev tests a number of different independent variables, including gender, exposure to conflict, distance from Chechnya’s capital (Groznyy), altitude (given cultural differences between upland and lowland Chechens [@mountain]) and various other variables on three indexes, which he labels indexRL, indexS and indexA. IndexRL, created by Lazarev early in the paper based on interview data, measures a given person’s likelihood to opt for Russian law, which indexS and indexA measure likelihood of sharia and adat, respectively. The author includes a number of graphics as well, including several ggplots, regression tables (created through stargazer) and others. Lazarev uses all of these methods to elucidate patterns in the data and arrive at his previously-described conclusions.

For my replications, I used R. The author's original code was in R as well, and had been posted on Harvard University's Dataverse.^[Data for this paper can be found at: https://dataverse.harvard.edu/dataset.xhtml?persistentId=doi:10.7910/DVN/KOVT5Y] As I show in my Tables and Figures section, I was able to replicate all of the main tables and graphics that Lazarev provides in his paper. The author's code was well-formatted, and all of the necessary data was included. I have included Lazarev's original data with my comments in my Github repository.^[All analysis for this paper is available under Milestone-3.Rmd in my github repo: https://github.com/dfshapir/Replication] 

To replicate Lazarev's findings, I had to make very few changes to Lazarev's code. The only aspects of Lazarev's code that did not work were a couple of formatting commands that were not compatible with my computer. However, they did not impact the resulting figures and graphics. Thus, in my extension to Lazarev's paper, instead of showing new results based on my replication, I decided to expand on Lazarev's work, using Bayes and the rstanarm package in R to supplement Lazarev's ordinary least squares linear regressions. Using Bayes, I re-evaluated several of Lazarev's most important figures in his paper and show my results in the "Extension" section. Overall, this analysis proves that Lazarev's results hold well, further confirming that his findings are important and hold weight. 

This paper also discusses themes that Lazarev brought up in his work and questions certain arguments that the author makes. This paper looks into Lazarev's usage of Ingushetia as a quasi-"control" with which to compare Chechnya and looks deeper into the nature of Chechen sharia law. Finally, the paper also discusses some questions regarding Lazarev's data usage, including some of his choices of variables and his selection of which specific court cases to analyze, and provides some potential areas for future expansion.

# Literature Review

There exists a fairly significant literature on Chechnya, both in the West and in Russia. Some have written historical or ethnographic works on Chechnya and its inhabitants; good examples of this include Amjad Jaimoukha’s work *The Chechens* and Sebastian Smith’s *Allah’s Mountains*. Various aspects of history and ethnography have been captured in a novelistic style as well; Tolstoy’s *Hadji Murat* (published posthumously) describes 19th-century relations between Russians and North Caucasians, while Anthony Marra’s *A Constellation of Vital Phenomena* paints a picture of more modern-day life in Chechnya through a novelistic lens as well. The largest segment of the canon, however, is devoted to descriptions of Chechnya’s most recent two wars.

In English-language literature, much of this segment is devoted to the military side of the war. Robert Schaefer’s *The Insurgency in Chechnya and the North Caucasus: from Gazavat to Jihad* discusses Chechen history and many details of Chechnya’s recent wars; Brian Glyn Williams published a book on Chechnya in 2015 entitled *Inferno in Chechnya: the Russian-Chechen Wars, the Al Qaeda Myth, and the Boston Marathon Bombings*. Additionally, Julie Wilhelmsen published an analysis of the interwar period (the late 1990s), entitled *Russia’s Securitization of Chechnya: How war became acceptable*. Other works have been published on this subject as well, including Thomas de Waal’s *A Small Victorious War*, Anatol Lieven’s *Chechnya: Tombstone of Russian Power* and Emma Gilligan’s *Terror in Chechnya*. Le Heurou, Merlin, Regamey and Sieca-Kozlowski’s compilation of various works entitled *Chechnya at War and Beyond* is another good resource for general wartime information.

The Russian-language literature is somewhat more diverse. The military analyses of the conflict are much more focused on first-person accounts, including works such as *Bitva za Chechnyu* by Chechens D. B. Abdurakhmanov and Ya. Z. Akhmadov and narrative compilations such as Boltunov, Kobyletskiy, Skira and Chachukh’s *Zhestokie uroki chechnskoy voyny* and Efimov, Mikhaylov, Zinov’ev and Kolomiets’s *Chechenskaya voyna: rabota nad oshibkami*, published by the same organization. Other public figures involved in the war wrote personal memoirs about the conflict as well, including Vladimir Zorin’s *Kremnistyy put’ k miru* and Ruslan Khasbulatov’s *Vzorvannaya zhizn’*. Olga Allenova describes women’s personal experiences in her work *Chechnya ryadom: voyna glazami zhenshchiny*, while Tanya Lokshina compiled a set of personal narratives entitled *Chechnya: zhizn’ na voyne*. 

Historical accounts also exist in Russian; Ibragimov authored a novel on Chechen experiences in World War II (*Chechenskaya Respublika v period Velikoy Otechestvennoy Voyny*), German Sadulaev wrote *Ya – Chechenets!* and Shakhrudin Gapurov wrote lengthy works both on 19th century Chechnya (*Chechnya v period Kavkazskoy voyny*), and on 18th-19th century Chechen history: *Rossiya i Chechnya: poslednyaya tret’ XVIII – pervaya polovina XIX veka.* 

The most significant factor that Russian-language writers have brought to the literature, however, is journalism. Two journalists stand out in their coverage of Chechnya over the years: Anna Politkovskaya and Elena Milashina. Politkovskaya was known for her in-depth, on-the-ground analyses of the situation in Chechnya, most specifically focusing on the Second Chechen War and its immediate aftermath. She wrote countless articles for the newspaper Novaya Gazeta, and published several books as well, including *A Dirty War*, published in 1999 first in Russian and translated to English, *Vtoraya Chechenskaya* (English variation: A Small Corner of Hell), and other books on Chechnya and the Putin regime. She was murdered in 2006; many suspect that Ramzan Kadyrov was behind her death, as she had consistently spoken out against the Kadyrov regime in her work. The second author, Milashina, also writes for Novaya Gazeta and has diligently covered Kadyrov and Chechnya since Politkovskaya’s murder. She was the first to break the story about Chechnya’s gay purges, and, while less internationally-renowned than Politkovskaya, Milashina is an outstanding Russian-language source (for accurate information on everything about Chechnya. There are obviously other journalists who cover Chechnya as well; these two, however, are by far the most well-known and have written countless lengthy pieces that have contributed significantly to the current understanding of Chechnya.

Aside from Allenova's and Lokshina's contributions, however, very little scholarly attention has been paid directly to the issue of legal pluralism in present-day Chechnya or gender issues. Cremer (2012) wrote on the role of customary law (adat) in Chechnya, and Gammer (2005) described the role of sharia in Chechnya and Dagestan. But both of these papers focused on singular types of law, not law in a comparative perspective, nor how gender issues play into legal choice. Lazarev's paper thereby fits into an important hole in the literature. Below, I quickly state my position on the replicability of Lazarev's paper, and then present my own extensions of Lazarev's work.

# Replication

As stated previously, I was able to replicate every aspect of Lazarev's paper. The only aspect of Lazarev's paper that was not perfectly replicable was the graphic that he labeled as Table 2 (in this paper labeled as Table 1). In this regression table, a few coefficients were around .001 off from Lazarev's original numbers. However, none of these slight discrepancies in any way change Lazarev's main conclusions. Overall, my replication was a success, and Lazarev's data-based conclusions hold steady with outside evaluation. As such, in my extension, I focus on ensuring that the results of Lazarev's regressions hold up under Bayesian analysis and critique Lazarev's analysis and data choices.

# Extension

My extension is split up into three sections. The first is devoted to Bayesian analysis, in which I run stan_glm() on all of Lazarev's OLS regressions to check if Lazarev's conclusions hold up. Next, I address some potential issues with Lazarev's analysis, dividing my evaluation into two separate critiques: analysis critiques and data critiques. These two categories overlap significantly, but I believe that splitting them up in such a way provides structure to the paper. In general, I believe that Lazarev comes to many convincing conclusions and uses data well to support his findings. Nonetheless, there are a few areas in which I believe that Lazarev could have been more thorough and/or where I believe that literature does not support Lazarev’s findings.

### Bayesian Regression

Lazarev has three sections in his code where he utilizes OLS regressions, labeled as Table 2, Table 3 and Table 4 in the data. I ran Bayesian analysis on these three Tables. First, I show the Bayesian regression equivalent for the figure that Lazarev labels as Table 2 in his data. This table measures how various variables are likely to effect a person's likelihood of choosing Russian Law, Sharia, or Adat. In his paper, Lazarev argues that women are much more likely to choose Russian law organs than men. Lazarev also includes various other independent variables, in addition to "female" in his regression, which I have included in the Bayesian regression as  well. The dependent variables are Lazarev's respective "indexes." I ran stan_glm() on Lazarev's variables, and put the resulting coefficients and error into a gt table for easy readibility.  

```{r include = FALSE, cache = TRUE}
set.seed(9)
upd_data <- read.csv2("raw-data/upd_wp_data_survey.csv")

stanl1 <- stan_glm(indexRL ~ killed + wounded + damaged + displaced + female + 
           as.factor(age_cohorts) + incomefull + edufull + unemployed + urban_com, data=upd_data, refresh = 0) 

tidystanl1 <- tidy(stanl1)

stanl2 <- stan_glm(indexS ~ killed + wounded + damaged + displaced + female + 
           as.factor(age_cohorts) + incomefull + edufull + unemployed + urban_com, data=upd_data, refresh = 0) 

tidystanl2 <- tidy(stanl2)

stanl3 <- stan_glm(indexA ~ killed + wounded + damaged + displaced + female + 
           as.factor(age_cohorts) + incomefull + edufull + unemployed + urban_com, data=upd_data, refresh = 0) 

tidystanl3 <- tidy(stanl3)
```

```{r graphics2}
tidytab2 <- cbind(tidystanl1, tidystanl2, tidystanl3)

tidytab2 <- tidytab2[,-c(4, 7)]

tidytab2 <- tidytab2 %>%
  mutate(Variable = term) %>%
  mutate(`Index Russian Law` = estimate) %>%
  mutate(`Error Russian Law` = std.error) %>%
  mutate(`Index Sharia` = estimate.1) %>%
  mutate(`Error Sharia` = std.error.1) %>%
  mutate(`Index Adat` = estimate.2) %>%
  mutate(`Error Adat` = std.error.2) %>%
  dplyr::select(Variable, `Index Russian Law`, `Error Russian Law`, `Index Sharia`, `Error Sharia`, `Index Adat`, `Error Adat`) %>%
  mutate(`Index Russian Law` = round(`Index Russian Law`, digits = 3)) %>%
  mutate(`Error Russian Law` = round(`Error Russian Law`, digits = 3)) %>%
  mutate(`Index Sharia` = round(`Index Sharia`, digits = 3)) %>%
  mutate(`Error Sharia` = round(`Error Sharia`, digits = 3)) %>%
  mutate(`Index Adat` = round(`Index Adat`, digits = 3)) %>%
  mutate(`Error Adat` = round(`Error Adat`, digits = 3))

tidytab2$Variable <- recode(tidytab2$Variable, `(Intercept)` = "Intercept",
                            `as.factor(age_cohorts)older` = "ageOlder",
                            `as.factor(age_cohorts)youth` = "ageYouth")
  
gttable2 <- tidytab2 %>% 
  gt() %>%
  tab_header(title = "Bayesian Regression of Lazarev Table 2",
             subtitle = "Data from Egor Lazarev") %>%
  as_latex()

gttable2
```

This table's results do not match Lazarev's results exactly. However, I believe that this is simply because they are different regressions, and because stan_glm() uses sampling, the chances of the stan_glm() coefficients matching the lm() coefficients exactly are very small. All coefficients here fall within the standard error of Lazarev's initial OLS regressions, and no patterns change. As such, I consider these results satisfactory.To further show how the coefficients match, I show here the spread of the coefficients for the relationship of the "female" variable and "indexRL"generated by my Bayesian regression.

```{r grph}
model_intercept <- tidystanl1$estimate[1]
model_slope <- tidystanl1$estimate[6]

draws <- spread_draws(stanl1, `(Intercept)`, `female`)

ggplot(upd_data, aes(x = female, y = indexRL)) +
  geom_jitter(width = 0.2) + 
  geom_abline(data = draws, aes(intercept = `(Intercept)`, slope = female), size = 0.1, alpha = 0.08, color = "skyblue") +
  geom_abline(intercept = model_intercept, slope = model_slope) +
  labs(title = "Relationship of Gender and Likelihood of Choosing Russian Law",
       subtitle = "Data from Egor Lazarev",
       x = "Gender (1 = Female, 0 = Male)",
       y = "Russian Law Choice Index")
```

As per a 2000 paper by King et al., this graphic focuses on a main point of Lazarev's piece (the relationship between gender and choice of legal system), shows uncertainty and presents results in a user-friendly manner [@manner]. The slope of this graph is about 0.09, meaning that women are estimated to be about 9 percent more likely to choose Russian law than men by my model. I include the distribution of slopes generated by my stan_glm() call, as represented by the blue lines surrounding the main slope.

Next, I show the Bayesian regression equivalent for the figure that Lazarev labels as Table 3 in his paper. Table 3 measures the effect of community victimization by violence in the war and gender on legal preference. Lazarev shows in his paper that not only are women more likely to choose Russian law organs, but the trend becomes even more apparent for women in communities victimized by violence. As such, he includes the "female" variable (for gender), the "com_exposure" variable (for a community's exposure to violence during the Chechen Wars) and the interaction between the two variables. My Bayesian table shows the same variables.

```{r tab3stan, cache = TRUE}
set.seed(9)
stank1 <- stan_glm(indexRL ~ com_exposure*female + 
           as.factor(age_cohorts) + incomefull + edufull + unemployed + urban_com + 
           russ_pop + lmaltitude + ldistance_Grozny + lcom_size + as.factor(rayon), data = upd_data, refresh = 0)
tidystank1 <- tidy(stank1)

stank2 <- stan_glm(indexS ~ com_exposure*female + 
           as.factor(age_cohorts) + incomefull + edufull + unemployed + urban_com + 
           russ_pop + lmaltitude + ldistance_Grozny + lcom_size + as.factor(rayon), data = upd_data, refresh = 0)
tidystank2 <- tidy(stank2)

stank3 <- stan_glm(indexA ~ com_exposure*female + 
           as.factor(age_cohorts) + incomefull + edufull + unemployed + urban_com + 
           russ_pop + lmaltitude + ldistance_Grozny + lcom_size + as.factor(rayon), data = upd_data, refresh = 0)
tidystank3 <- tidy(stank3)
```

```{r}
tidytab3 <- cbind(tidystank1, tidystank2, tidystank3)

tidytab3 <- tidytab3[c(1:3, 27),-c(4, 7)]

tidytab3 <- tidytab3 %>%
  mutate(Variable = term) %>%
  mutate(`Index Russian Law` = estimate) %>%
  mutate(`Error Russian Law` = std.error) %>%
  mutate(`Index Sharia` = estimate.1) %>%
  mutate(`Error Sharia` = std.error.1) %>%
  mutate(`Index Adat` = estimate.2) %>%
  mutate(`Error Adat` = std.error.2) %>%
  dplyr::select(Variable, `Index Russian Law`, `Error Russian Law`, `Index Sharia`, `Error Sharia`, `Index Adat`, `Error Adat`) %>%
  mutate(`Index Russian Law` = round(`Index Russian Law`, digits = 3)) %>%
  mutate(`Error Russian Law` = round(`Error Russian Law`, digits = 3)) %>%
  mutate(`Index Sharia` = round(`Index Sharia`, digits = 3)) %>%
  mutate(`Error Sharia` = round(`Error Sharia`, digits = 3)) %>%
  mutate(`Index Adat` = round(`Index Adat`, digits = 3)) %>%
  mutate(`Error Adat` = round(`Error Adat`, digits = 3))

tidytab3$Variable <- recode(tidytab3$Variable, `(Intercept)` = "Intercept",
                            `com_exposure` = "exposure",
                            `com_exposure:female` = "exp:female")

gttable3 <- tidytab3 %>% 
  gt() %>%
  tab_header(title = "Bayesian Regression of Lazarev Table 3",
             subtitle = "Data from Egor Lazarev") %>%
  as_latex()

gttable3
```

As with the previous table, stan_glm() outputs very similar coefficients to a regular OLS regression, strengthening Lazarev's conclusions.

Finally, I run Bayesian regressions for the variables described in Table 4. Table 4 in Lazarev's paper is constructed a bit differently than the other two tables, as Lazarev uses the istez_females variables as his dependent variable, which is binary ("itsets" meaning "plaintiff" in Russian). As such, Lazarev constructs three logistic regressions, measuring how likely it is that the plaintiff is female in a) all court cases in Chechnya over a given time period with individual plaintiffs, b) all of these cases that deal with family-related matters, and c) all of these cases that do not deal with family-related matters. In the article, we see that women are much more likely to be the plaintiff in family-related cases that in non-family-related cases, and that factors such as community vicitimization enhance this effect. I ran Bayesian regressions on Lazarev's data for these factors, and got similar results, showing again the strength of Lazarev's results.

```{r tab4stan, cache = TRUE}
set.seed(9)
reg_data <- read.csv2("raw-data/wp_data_courts.csv")

famdata <- reg_data[which(reg_data$family==1),]
nonfamdata <- reg_data[which(reg_data$family==0),]

stanm1 <- stan_glm(istez_females ~ com_exposure + urban +
            mountainous + russ_pop + pop_fem_share + 
            as.factor(year),family=binomial(link='logit'),data = reg_data, refresh = 0)
tidystanm1 <- tidy(stanm1)

stanm2 <- stan_glm(istez_females ~ com_exposure + urban +
            mountainous + russ_pop + pop_fem_share + 
            as.factor(year),family=binomial(link='logit'),data=famdata, refresh = 0)
tidystanm2 <- tidy(stanm2)

stanm3 <- stan_glm(istez_females ~ com_exposure + urban +
            mountainous + russ_pop + pop_fem_share + 
            as.factor(year),family=binomial(link='logit'),data=nonfamdata, refresh = 0)
tidystanm3 <- tidy(stanm3)
```

```{r tidytab4}
tidytab4 <- cbind(tidystanm1, tidystanm2, tidystanm3)

tidytab4 <- tidytab4[1:6,-c(4, 7)]

tidytab4 <- tidytab4 %>%
  mutate(Variable = term) %>%
  mutate(`All Cases` = estimate) %>%
  mutate(`Error All Cases` = std.error) %>%
  mutate(`Family Cases` = estimate.1) %>%
  mutate(`Error Family Cases` = std.error.1) %>%
  mutate(`Other Cases` = estimate.2) %>%
  mutate(`Error Other Cases` = std.error.2) %>%
  dplyr::select(Variable, `All Cases`, `Error All Cases`, `Family Cases`, `Error Family Cases`, `Other Cases`, `Error Other Cases`) %>%
  mutate(`All Cases` = round(`All Cases`, digits = 3)) %>%
  mutate(`Error All Cases` = round(`Error All Cases`, digits = 3)) %>%
  mutate(`Family Cases` = round(`Family Cases`, digits = 3)) %>%
  mutate(`Error Family Cases` = round(`Error Family Cases`, digits = 3)) %>%
  mutate(`Other Cases` = round(`Other Cases`, digits = 3)) %>%
  mutate(`Error Other Cases` = round(`Error Other Cases`, digits = 3))

tidytab4$Variable <- recode(tidytab4$Variable, `(Intercept)` = "Intercept",
                            `com_exposure` = "exposure",
                            `pop_fem_share` = "fem_share")

gttable4 <- tidytab4 %>% 
  gt() %>%
  tab_header(title = "Bayesian Regression of Lazarev Table 4",
             subtitle = "Data from Egor Lazarev") %>%
  as_latex()

gttable4
```

In total, Bayesian analysis of Lazarev's results confirmed and strengthened the author's findings. Regarding reproducibility and accuracy of reporting results, Lazarev does an excellent job. As such, I have devoted the next sections to discussions not of Lazarev's code or his results, but of his analysis and data. 

#### Analysis critiques

First of all, I believe that Lazarev oversimplifies sharia’s resurgence and role in Chechnya. He largely seems to place the promotion of sharia in modern-day Chechnya as a patriarchal response to increased women’s empowerment in Chechnya following the wars. While I understand the author's point, I believe that glosses over some other main reasons behind why Kadyrov started to re-emphasize sharia in the first place, thereby relying on gender as a driver a bit more heavily than necessary. After the Second Chechen War and the re-integration of Chechnya, Kadyrov was tasked with putting Chechnya back together. In this process, he had to negotiate with rebel Islamists and cajole them into rejoining society. Lazarev paints Chechnya’s re-Islamicization as a patriarchal reaction to a system in which women had more power in society. While this certainly may have been part of it, I believe that the political gymnastics necessary to persuade this radicalized portion of Chechnya to return to society was an equally (if not more) important driver. Ramzan’s retraditionalization of societal norms was a key factor in weakening the pull of the radical insurgency: Even if some rebel fighters believed that an independent Chechnya was doomed to fail, they would still support the insurgency because they believed that conservative Islam was right for Chechnya, especially in the face of “godless” Russia, and that a Chechnya within Russia would be forced to submit to Russian authority and potentially even give up its religion, as was the case in the Soviet Union. But by establishing Chechnya as a more conservative Islamic republic and tightening Chechnya’s societal laws, Kadyrov showed radicalized Chechens that it is indeed possible to exist inside Russia and still observe traditional, conservative Islam. For insurgency leaders, this posed a huge problem: how can one propagate an anti-Russia, anti-Kadyrov message when the Kadyrov regime has in fact implemented many of the ideologies that the insurgency wanted? I therefore believe that the switch to promoting a “macho” form of sharia was a strategic decision based not so much on stemming the rise of women into important positions in Chechnya, but on convincing radicalized and overwhelmingly male ex-fighters that insurgency was *not necessary*, because the new Chechnya would be based on a similar moral framework to the one that existed in the insurgency—simply inside Russia instead of outside it. While the data that Lazarev provides definitely supports his argument about the split in gender, I am somewhat worried that the author leans too heavily at times on gender as a driver of policy, especially regarding the re-establishment of sharia.

Secondly, Lazarev writes that “at the macro level, the gender gap in legal preferences is largely driven by men.” A number of questions spring from this statement: Does this claim undercut the whole argument of women’s empowerment? Is it really women who are making the decisions or men? Here, I think it’s important to return to Lazarev’s admittance in a small footnote that he “understand[s] women’s empowerment in a rather thin way—as an outcome of the process of transformation of gender roles characterized by an increase in women’s sense of agency, social status, material resources, and access to political and legal institutions.” It seems that this statement fits Lazarev’s definition; if women simply *sense* that they have more agency, then the results fit. Furthermore, at the macro level in Chechnya, essentially everything is largely driven by men as it is, so this statement should not come as a surprise. This aspect of Lazarev’s argument, therefore, does not necessarily undercut his argument, but it does highlight his relatively weak definition of women’s empowerment, which, while certainly driven by the realities on the ground in Chechnya, perhaps deserves further examination. 

Finally, regarding comparisons between Chechnya and neighboring Ingushetia, Lazarev argues generally that “comparative analysis at the macro level indicates no comparable gender differences in legal preferences in Ingushetia. Thus, the results of my analyses converge to show that conflict in Chechnya disrupted gender hierarchies.” However, while Chechens and Ingush are indeed very similar ethnically, a history of conflict was by no means the only thing dividing Ingushetia and Chechnya at the time that this paper was published. Chechnya was (and still is) led by Ramzan Kadyrov, who, as Lazarev mentions in his piece, actively promotes a conservative Islamic lifestyle mixed with a healthy dose of machismo. Ingushetia, on the other hand, had a very different leadership situation, which Lazarev left out: Then-head of Ingushetia Yunus-Bek Evkurov was an ex-military man who generally acted as the Kremlin dictated and certainly did not go out of his way to post masculine workout videos on social media or actively promote conservative Islam. While non-state law definitely has its place in Ingush society, its promotion is less intimately tied to hypermasculinity as in Chechnya, where Ramzan Kadyrov ensures that the two are inextricably intertwined. Furthermore, an in-depth study of women’s legal organ choices in family law matters in Ingushetia by Izabella Evloeva in 2019 (after this article was published) shows that in Ingushetia, in fact, mothers often tend to *prefer* sharia courts in family matters [@Ingush]. Clearly, there is more nuance to the Ingushetia-Chechnya comparison that meets the eye.

#### Data critiques:

One critique that I have for Lazarev’s data is regarding his treatment of Chechnya’s geography. On page 680, Lazarev notes in a footnote that his analysis excludes a few mountainous regions of Chechnya, stating that they are “mostly uninhabited mountainous areas.” While Lazarev is not wrong that these areas have very few people, I wonder about what would happen if they were included in the data: after all, these regions have been much more important in Chechnya’s recent history than their low populations would imply, as some of them are well-known as being a main source of anti-state sentiments: Sharoy rayon, for example, was a hiding place for many Islamist rebels during the wars. 

Additionally, regarding variable choice, I think that altitude is a much more important variable here than “distance from Groznyy.” Altitude really matters – the culture of mountainous Chechnya is much different than that of lowland Chechnya. Distance from Groznyy, on the other hand, is in my opinion a somewhat weak variable. Lazarev’s idea is that Groznyy was the area that all forces were pushing to control, thereby making it the epicenter of conflict. But the conflict was unequally spread: Throughout the course of the war, a lot of areas that are near Groznyy were nearly untouched by the war, because they were occupied by forces loyal to the federal center from very close to the beginning. The Kadyrov clan hails from Kurchaloi rayon and controlled Gudermes along with the Yamadaev family, thereby ensuring safety for these areas, as both families allied with the Russian center early on in the Second Chechen War. These areas are quite close to Groznyy – only about 25 miles away. Meanwhile, a lot of northern Chechnya (significantly farther from Groznyy) was hit significantly less hard. Furthermore, equidistant parts of northern and southern Chechnya were affected in very different ways by the war—the southern mountains acted as much more of a hideout than the northern steppes. I am not confident that “distance from Groznyy” is a particularly useful variable, and I think that the altitude variable that Lazarev uses is significantly more important.

Thirdly, there were 106,000 court cases in magistrates’ courts in Chechnya from 2010-2016. He only used 9,000 of them, in which the plaintiff was a natural person. Of these, 60% were family-oriented. Among family-oriented cases in this time period, perhaps Lazarev’s data holds strong. But the fact that Lazarev only applies his findings to around 5% of Chechnya’s court cases, it is worth questioning how broadly applicable this data is.  

Finally, there are a few smaller areas that I believe should be explored further. For one, there is vast heterogeneity in age, location, and other factors among women that is worth analyzing. Also, Lazarev only Chechnya and Ingushetia through his indexRL variable (Russian law), and not for indexS or indexA. It would be interesting to see how these variables are connected as well. 

#### Conclusion

Overall, Lazarev does an excellent job with his data, and his code is easily replicable and provides the same results shown in his paper. I believe that this article was well-researched, and the broader conclusions are interesting, applicable and should be taken seriously. However, there are a few areas in which I believe that the article could improve, which this section has highlighted and expanded upon.

\pagebreak
# Tables and Figures

This section shows my replications of Lazarev's graphs and tables. This first graph is labeled as Figure 3 in Lazarev's paper. 

```{r graphic, message = FALSE, warning = FALSE}
# I commented out this whole code in my Milestone-3.Rmd in the Figure 3 section. I made a few changes for the purposes of this assignment, which I have indicated in this code chunk. 

fig3dat <- read.csv2("raw-data/upd_wp_data_survey.csv")

range01 <- function(x) {(x - min(x))/(max(x) - min(x))}

require(plyr)
length2 <- function (x, na.rm=FALSE) {
  if (na.rm) sum(!is.na(x))
  else       length(x)
}

if (!require(pacman)) install.packages("pacman")

pacman::p_load(readr, ggplot2, plyr, dplyr, magrittr, tidyr, purrr, ggthemes)

means1 <- round(tapply(fig3dat$indexRL, fig3dat$female, mean, na.rm = T), digits=3)
sds1 <- round(tapply(fig3dat$indexRL, fig3dat$female, sd, na.rm = T), digits=3)
n1 <- tapply(fig3dat$indexRL, fig3dat$female, length2, na.rm = T)

se1 <- round(sds1/sqrt(n1), digits=3)

error1 <- round((qt(0.975,df=n1-1)*se1), digits = 3)

min <- c(0,1)
object1 <- c(1,1)

means2 <- round(tapply(fig3dat$indexS, fig3dat$female, mean, na.rm = T), digits=3)
sds2 <- round(tapply(fig3dat$indexS, fig3dat$female, sd, na.rm = T), digits=3)
n2 <- tapply(fig3dat$indexS, fig3dat$female, length2, na.rm = T)
se2 <- round(sds2/sqrt(n2), digits=3)
error2 <- round((qt(0.975,df=n2-1)*se2), digits = 3)
object2 <- c(2,2)

means3 <- round(tapply(fig3dat$indexA, fig3dat$female, mean, na.rm = T), digits=3)
sds3 <- round(tapply(fig3dat$indexA, fig3dat$female, sd, na.rm = T), digits=3)
n3 <- tapply(fig3dat$indexA, fig3dat$female, length2, na.rm = T)
se3 <- round(sds3/sqrt(n3), digits=3)
error3 <- round((qt(0.975,df=n3-1)*se3), digits = 3)
object3 <- c(3,3)

V1_dat <- rbind(cbind(object1, min, means1, sds1, n1, se1, error1, deparse.level=0),
                cbind(object2, min, means2, sds2, n2, se2, error2, deparse.level=0),
                cbind(object3, min, means3, sds3, n3, se3, error3, deparse.level=0))

rownames(V1_dat) <- c(1:6) 
colnames(V1_dat) <- c("sum", "min", "put", "sds", "n", "se", "error") 
sb <- as.data.frame(V1_dat)

sb2 <- sb

sb2$min <- as.factor(sb2$min) 
sb2$sum <- as.factor(sb2$sum)
levels(sb2$sum) <- c("State Law", "Sharia", "Adat") 

figure3 <- ggplot(sb2, aes(x=sum, y=put, fill = min)) + 
  geom_bar(position=position_dodge(), 
           stat="identity", size=.3) + 
  geom_errorbar(aes(ymin=put-error, ymax=put+error),
                size=.5,    
                width=.3,
                position=position_dodge(.9)) +
  
# Added titles and axis labels, changed to labs() instead of xlab(), ylab() and ggtitle()
  
  labs(title = "FIGURE 3: How Gender Impacts Choice of Legal System",
       subtitle = "Data From Lazarev, 'Laws in Conflict: Legacies of War, Gender, and Legal Pluralism in Chechnya'",
       x = "Legal System",
       y = "Mean of Index",
       caption = "This data is taken from surveys performed by Lazarev during fieldwork. Indexes are calculated by averaging \nthe number of scenarios where participants respond that they would choose one form of law over another. Lazarev's \ndata shows gender-based trends in choice of legal structure in Chechnya. The graph shows how men and women \ndiffer in their respective likelihoods to choose Russian state law, sharia, and adat. Women are much more likely \nto choose Russian law than men are, while men are somewhat more likely to choose sharia or adat. The error \nbars are included as well to show the uncertainty around the means.") +
  coord_cartesian(ylim=c(0, .5))+  
  scale_y_continuous(breaks=seq(0, 0.5, .1)) +
  scale_fill_manual(name="Gender", 
                    breaks=c("0", "1"), 
                    labels=c("Male", 
                             "Female"),
                    
# Capitalized legend labels

                    values=c("cornsilk3", "gray33")) +
  theme(text = element_text(size = 10),
        
# Changed text size
        
  axis.line = element_line(colour = "black"),

# Kept axis title

        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
  plot.caption = element_text(hjust = 0.5))

figure3
```
\pagebreak

This next figure is labeled as Table 2 in the article. 

```{r include = FALSE}
upd_data <- read.csv2("raw-data/upd_wp_data_survey.csv")

l1 <- lm(indexRL ~ killed + wounded + damaged + displaced + female + 
           as.factor(age_cohorts) + incomefull + edufull + unemployed + urban_com, data=upd_data) 
summary(l1) 

l2 <- lm(indexS ~ killed + wounded + damaged + displaced + female + 
           as.factor(age_cohorts) + incomefull + edufull + unemployed + urban_com, data=upd_data) 
summary(l2) 

l3 <- lm(indexA ~ killed + wounded + damaged + displaced + female + 
           as.factor(age_cohorts) + incomefull + edufull + unemployed + urban_com, data=upd_data) 
summary(l3) 
```

```{r table2, results = "asis"}
stargazer(l1, l2, l3, title="OLS Regression Analysis of the Impact of Victimization on Legal Preferences", 
          type = "latex",
          header = FALSE)
```

*This table confirms and expands upon the data presented in FIGURE 3. The coefficients corresponding to the "female" variable correspond to the trends portrayed graphically, showing that being women are significantly more likely to choose state law than men, slightly less likely than men to choose sharia, and significantly less likely to choose adat than men. The table also accounts for other variables: if an individual had a relative killed or wounded, if the person has been displaced, and other variables. The regression table also shows how income, education, unemployment and urbanity affect choice of one law style over another.*

This next table was labeled as Table 3 in the article.

```{r tab3prep, include = FALSE}
k1 <- lm(indexRL ~ com_exposure*female + 
           as.factor(age_cohorts) + incomefull + edufull + unemployed + urban_com + 
           russ_pop + lmaltitude + ldistance_Grozny + lcom_size + as.factor(rayon), data = upd_data)
summary(k1)

k1_vcov <- cluster.vcov(k1, upd_data$location)

coeftest(k1, vcov. = k1_vcov)

cluster_se <- sqrt(diag(cluster.vcov(k1, upd_data$location)))

k2 <- lm(indexS ~ com_exposure*female + 
           as.factor(age_cohorts) + incomefull + edufull + unemployed + urban_com + 
           russ_pop + lmaltitude + ldistance_Grozny + lcom_size + as.factor(rayon), data = upd_data)
summary(k2)

k2_vcov <- cluster.vcov(k2, upd_data$location)

coeftest(k2, vcov. = k2_vcov)

cluster_se <- sqrt(diag(cluster.vcov(k2, upd_data$location)))

k3 <- lm(indexA ~ com_exposure*female + 
           as.factor(age_cohorts) + incomefull + edufull + unemployed + urban_com + 
           russ_pop + lmaltitude + ldistance_Grozny + lcom_size + as.factor(rayon), data = upd_data)
summary(k3)

k3_vcov <- cluster.vcov(k3, upd_data$location)

coeftest(k3, vcov. = k3_vcov)

cluster_se <- sqrt(diag(cluster.vcov(k2, upd_data$location)))

```

```{r tab3, results = "asis"}

stargazer(k1, k2, k3, se = list(coeftest(k1, vcov. = k1_vcov)[,2],
                                coeftest(k2, vcov. = k2_vcov)[,2],
                                coeftest(k3, vcov. = k3_vcov)[,2]),
          title = "OLS Regression Analysis of the Effect of Community Victimization and Gender on Legal Preferences",
          type = "latex",
          header = FALSE,
          keep = c("\\bcom_exposure\\b", "\\bfemale\\b", "\\bConstant\\b"))

# Formatted to make it look more like his table

```
*This table moves the narrative toward Lazarev's next argument, namely, that the pattern of women choosing to turn to state courts for legal disputes rather than sharia or customary courts is exacerbated  by the level to which a region was aﬀected by violence during the Chechen wars. Conﬂict provided women with more opportunity to pursue their interests through oﬃcial law. The table shows that when a given person is female and lives in a community affected by violence, the person is 6 percent more likely to choose state law, and almost 7 percent less likely to choose sharia (with a certain degree of error). Both of these numbers show how the conflict experience, in Lazarev's view, plays a role in gendered legal choice.*

\pagebreak
This next graph is Figure 5, showing differences in victimization and nonvictimization. 

```{r include = FALSE}
fig5data <- read.csv2("raw-data/upd_wp_data_survey.csv")

fig5data$victimized[fig5data$com_exposure=='0']<-'nonvictimized'
fig5data$victimized[fig5data$com_exposure=='1']<-'victimized'

fig5data$gender[fig5data$female=='0']<-'male'
fig5data$gender[fig5data$female=='1']<-'female'

m1 <- lm(indexRL ~ victimized*gender + 
           as.factor(age_cohorts) + incomefull + edufull + unemployed + urban_com +
           russ_pop + lmaltitude + ldistance_Grozny + lcom_size, data = fig5data)
summary(m1)

figure5 <- cat_plot(m1, pred = victimized, modx = gender, geom = "bar") + 
  labs(x="", y = "", title = "FIGURE 5: Interaction Plot for the Effects of Community \nVictimization and Gender on Support for State Law",
       caption = "This plot shows the difference in the gender split regarding support for state law between \ncommunities that were victimized and not victimized by violence. In communities victimized by \nviolence, Lazarev shows that women are much more likely to choose state law than men are, and the \ndivide between genders is significantly greater than the divide in communities that have not been \nvictimized by violence. This graph corresponds with Table 3, which shows the interaction \nbetween the 'com_exposure' variable and the 'female' variable. Not only is Lazarev arguing that \nwomen are more likely to choose state law than men -- he is also showing that being exposed to \nviolence has an effect as well, as split is wider in victimized areas than non-victimized ones. \nThis, in his eyes, shows support for the idea that much of the split is due to conflict.") +
  scale_color_manual("gender", values=c('grey20','grey60'))+
  scale_fill_manual("gender",values=c('grey30','grey80')) +
  theme(plot.caption = element_text(hjust = 0.5))
``` 

```{r}
figure5
```

\pagebreak
This table was originally labeled as Table 3 in Lazarev's code; in the paper, it is labeled as Table 4.

```{r include = FALSE}
reg_data <- read.csv2("raw-data/wp_data_courts.csv")

# I changed the name of the data from his original. I also put include = FALSE so that this all would not show up in the PDF, but I could make a table out of it. 

famdata <- reg_data[which(reg_data$family==1),]
nonfamdata <- reg_data[which(reg_data$family==0),]

m1 <- glm(istez_females ~ com_exposure + urban +
            mountainous + russ_pop + pop_fem_share + 
            as.factor(year),family=binomial(link='logit'),data = reg_data)
summary(m1)

m1_vcov <- cluster.vcov(m1, reg_data$uchastok)

coeftest(m1, vcov. = m1_vcov)

cluster_se <- sqrt(diag(cluster.vcov(m1, reg_data$uchastok)))

stargazer(m1, se = list(coeftest(m1, vcov. = m1_vcov)[,2]), 
          omit.stat = c("rsq", "f", "adj.rsq", "ser"))

m2 <- glm(istez_females ~ com_exposure + urban +
            mountainous + russ_pop + pop_fem_share + 
            as.factor(year),family=binomial(link='logit'),data=famdata)
summary(m2)

m2_vcov <- cluster.vcov(m2, famdata$uchastok)

coeftest(m2, vcov. = m2_vcov)

cluster_se <- sqrt(diag(cluster.vcov(m2, famdata$uchastok)))

m3 <- glm(istez_females ~ com_exposure + urban +
            mountainous + russ_pop + pop_fem_share + 
            as.factor(year),family=binomial(link='logit'),data=nonfamdata)
summary(m3)

m3_vcov <- cluster.vcov(m3, nonfamdata$uchastok)

coeftest(m3, vcov. = m3_vcov)

cluster_se <- sqrt(diag(cluster.vcov(m3, nonfamdata$uchastok)))
```

```{r tab4, results = "asis"}
stargazer(m1, m2, m3, se = list(coeftest(m1, vcov. = m1_vcov)[,2],
                                coeftest(m2, vcov. = m2_vcov)[,2],
                                coeftest(m3, vcov. = m3_vcov)[,2]),
          title = "Predicting Female Plaintiff in Civil Disputes: Binary Logistic Regression",
          type="latex", 
          header = FALSE,
          keep = c("\\bcom_exposure\\b", "\\burban\\b", "\\bmountainous\\b", "\\bruss_pop\\b", "\\bpop_fem_share\\b", "\\bConstant\\b"))
```
*This table shows various predictors for whether or not the plaintiff will be female in a given state law court case ("istez_females" means female plaintiffs). Lazarev takes all court cases over a given postwar period in Chechnya that have an individual plaintiff and separates them into three categories. (1) shows results for all cases, (2) shows results for that subset that deals with "family issues" and (3) deals with the remainder, that is, the cases that are not family-related. Referring to this table, Lazarev argues that "all else being equal, in more victimized communities, the likelihood of having a female plaintiff is significantly higher than in less-victimized ones. Transformation of the logistic regression coefficient suggests that the difference is approximately 12 percentage points, which is substantially large." Lazarev also notes through this graph that simple male/female demographics (labeled as pop_fem_share) do not have predictive power, as error is very high. Thus, Lazarev shows through this table that there is a positive relationship between community victimization and subsequent use of state law by women.*

\pagebreak
This page displays a series of graphs that show up as Figure 2 in the article. I used the ggarrange() function in the ggpubr package.
```{r include = FALSE}
figdat <- read.csv2("raw-data/wp_data_raw.csv")
```

```{r, fig.width = 10, fig.height = 12}
h1 <- ggplot(data=figdat[!is.na(figdat$Q1),], 
             aes(factor(Q1))) + 
  geom_bar(aes(y = (..count..)/sum(..count..)),
           fill=("grey69"), position = "dodge") + 
  geom_text(aes(y = ((..count..)/sum(..count..)), 
                label = round((..count..)/sum(..count..), digits = 2)), 
            stat = "count", vjust = -0.25, size = 8) +
  scale_y_continuous(limits=c(0, .8)) +
  scale_x_discrete(labels=c("1" = "State Law","2" = "Sharia","3" = "Adat", "4" = "Don't Know")) +
  labs(title = "Child Custody",
       y = "Share",
       x = "")

h2 <- ggplot(data=figdat[!is.na(figdat$Q3_graph),], 
             aes(factor(Q3_graph))) + 
  geom_bar(aes(y = (..count..)/sum(..count..)),
           fill=("grey69"), position = "dodge") + 
  geom_text(aes(y = ((..count..)/sum(..count..)), 
                label = round((..count..)/sum(..count..), digits = 2)), 
            stat = "count", vjust = -0.25, size = 8) +
  scale_y_continuous(limits=c(0, .8)) +
  scale_x_discrete(labels=c("1" = "State Law","2" = "Sharia","3" = "Adat", "4" = "Don't Know")) +
  labs(title = "Domestic Violence",
       y = "Share",
       x = "")

h3 <- ggplot(data=figdat[!is.na(figdat$Q5_graph),], 
             aes(factor(Q5_graph))) + 
  geom_bar(aes(y = (..count..)/sum(..count..)),
           fill=("grey69"), position = "dodge") + 
  geom_text(aes(y = ((..count..)/sum(..count..)), 
                label = round((..count..)/sum(..count..), digits = 2)), 
            stat = "count", vjust = -0.25, size = 8) +
  scale_y_continuous(limits=c(0, .8)) +
  scale_x_discrete(labels=c("1" = "State Law","2" = "Sharia","3" = "Adat", "4" = "Don't Know")) +
  labs(title = "Bride Kidnapping",
       y = "Share",
       x = "")

h4 <- ggplot(data=figdat[!is.na(figdat$Q8_graph),], 
             aes(factor(Q8_graph))) + 
  geom_bar(aes(y = (..count..)/sum(..count..)),
           fill=("grey69"), position = "dodge") + 
  geom_text(aes(y = ((..count..)/sum(..count..)), 
                label = round((..count..)/sum(..count..), digits = 2)), 
            stat = "count", vjust = -0.25, size = 8) +
  scale_y_continuous(limits=c(0, .8)) +
  scale_x_discrete(labels=c("1" = "State Law","2" = "Sharia","3" = "Adat", "4" = "Don't Know")) +
  labs(title = "Honor Killing",
       y = "Share",
       x = "")

h5 <- ggplot(data=figdat[!is.na(figdat$Q10),], 
             aes(factor(Q10))) + 
  geom_bar(aes(y = (..count..)/sum(..count..)),
           fill=("grey69"), position = "dodge") + 
  geom_text(aes(y = ((..count..)/sum(..count..)), 
                label = round((..count..)/sum(..count..), digits = 2)), 
            stat = "count", vjust = -0.25, size = 8) +
  scale_y_continuous(limits=c(0, .8)) +
  scale_x_discrete(labels=c("1" = "State Law","2" = "Sharia","3" = "Adat", "4" = "Don't Know")) +
  labs(title = "Polygamy",
       y = "Share",
       x = "")

h6 <- ggplot(data=figdat[!is.na(figdat$Q12),], 
             aes(factor(Q12))) + 
  geom_bar(aes(y = (..count..)/sum(..count..)),
           fill=("grey69"), position = "dodge") + 
  geom_text(aes(y = ((..count..)/sum(..count..)), 
                label = round((..count..)/sum(..count..), digits = 2)), 
            stat = "count", vjust = -0.25, size = 8) +
  scale_y_continuous(limits=c(0, .8)) +
  scale_x_discrete(labels=c("1" = "State Law","2" = "Sharia","3" = "Adat", "4" = "Don't Know")) +
  labs(title = "Inheritance",
       y = "Share",
       x = "")

h7 <- ggplot(data=figdat[!is.na(figdat$Q14),], 
             aes(factor(Q14))) + 
  geom_bar(aes(y = (..count..)/sum(..count..)),
           fill=("grey69"), position = "dodge") + 
  geom_text(aes(y = ((..count..)/sum(..count..)), 
                label = round((..count..)/sum(..count..), digits = 2)), 
            stat = "count", vjust = -0.25, size = 8) +
  scale_y_continuous(limits=c(0, .8)) +
  scale_x_discrete(labels=c("1" = "State Law","2" = "Sharia","3" = "Adat", "4" = "Don't Know")) +
  labs(title = "Property",
       y = "Share",
       x = "")

h8 <- ggplot(data=figdat[!is.na(figdat$Q16),], 
             aes(factor(Q16))) + 
  geom_bar(aes(y = (..count..)/sum(..count..)),
           fill=("grey69"), position = "dodge") + 
  geom_text(aes(y = ((..count..)/sum(..count..)), 
                label = round((..count..)/sum(..count..), digits = 2)), 
            stat = "count", vjust = -0.25, size = 8) +
  scale_y_continuous(limits=c(0, .8)) +
  scale_x_discrete(labels=c("1" = "State Law","2" = "Sharia","3" = "Adat", "4" = "Don't Know")) +
  labs(title = "Car Accident",
       y = "Share",
       x = "")

h9 <- ggplot(data=figdat[!is.na(figdat$Q18),], 
             aes(factor(Q18))) + 
  geom_bar(aes(y = (..count..)/sum(..count..)),
           fill=("grey69"), position = "dodge") + 
  geom_text(aes(y = ((..count..)/sum(..count..)), 
                label = round((..count..)/sum(..count..), digits = 2)), 
            stat = "count", vjust = -0.25, size = 8) +
  scale_y_continuous(limits=c(0, .8)) +
  scale_x_discrete(labels=c("1" = "State Law","2" = "Sharia","3" = "Adat", "4" = "Don't Know")) +
  labs(title = "Debt",
       y = "Share",
       x = "")

h10 <- ggplot(data=figdat[!is.na(figdat$Q20),], 
              aes(factor(Q20))) + 
  geom_bar(aes(y = (..count..)/sum(..count..)),
           fill=("grey69"), position = "dodge") + 
  geom_text(aes(y = ((..count..)/sum(..count..)), 
                label = round((..count..)/sum(..count..), digits = 2)), 
            stat = "count", vjust = -0.25, size = 8) +
  scale_y_continuous(limits=c(0, .8)) +
  scale_x_discrete(labels=c("1" = "State Law","2" = "Sharia","3" = "Adat", "4" = "Don't Know")) +
  labs(title = "Murder",
       y = "Share",
       x = "")

ggarrange(h1, h2, h3, h4, h5, h6, h7, h8, h9, h10,
          ncol = 2, nrow = 5)
```

\pagebreak


\pagebreak
The final graph that the author uses is this comparison of how men and women view Russian state law in Chechnya and Ingushetia, comparatively. The replicated graph matches the one in the article. 
```{r}
total <- read.csv2("raw-data/wp_data_Chechnya_Ingushetia.csv")

ftotal <- total[which(total$data.female==1),]
mtotal <- total[which(total$data.female==0),]

means1 <- round(tapply(ftotal$data.indexRL, ftotal$chechnya, mean, na.rm = T), digits=3)
sds1 <- round(tapply(ftotal$data.indexRL, ftotal$chechnya, sd, na.rm = T), digits=3)
n1 <- tapply(ftotal$data.indexRL, ftotal$chechnya, length2, na.rm = T)
se1 <- round(sds1/sqrt(n1), digits=3)
error1 <- round((qt(0.975,df=n1-1)*se1), digits = 3)
min <- c(0,1)
object1 <- c(1,1)

means2 <- round(tapply(mtotal$data.indexRL, mtotal$chechnya, mean, na.rm = T), digits=3)
sds2 <- round(tapply(mtotal$data.indexRL, mtotal$chechnya, sd, na.rm = T), digits=3)
n2 <- tapply(mtotal$data.indexRL, mtotal$chechnya, length2, na.rm = T)
se2 <- round(sds2/sqrt(n2), digits=3)
error2 <- round((qt(0.975,df=n2-1)*se2), digits = 3)
min <- c(0,1)
object2 <- c(2,2)

V1_dat <- rbind(cbind(object1, min, means1, sds1, n1, se1, error1, deparse.level=0),
                cbind(object2, min, means2, sds2, n2, se2, error2, deparse.level=0))

rownames(V1_dat) <- c(1:4) 
colnames(V1_dat) <- c("sum", "min", "put", "sds", "n", "se", "error") 
sb <- as.data.frame(V1_dat)

sb2 <- sb
sb2$min <- as.factor(sb2$min) 
sb2$sum <- as.factor(sb2$sum)
levels(sb2$sum) <- c("Women", "Men") 

figure6 <- ggplot(sb2, aes(x=sum, y=put, fill = min)) + 
  geom_bar(position=position_dodge(), 
           stat="identity", size=.3) +      
  geom_errorbar(aes(ymin=put-error, ymax=put+error),
                size=.5,    # Thinner lines
                width=.3,
                position=position_dodge(.9)) +
  xlab("") +
  ylab("") +
  ggtitle("Gender Gaps in Support for State Law in Chechnya and Ingushetia") +
  coord_cartesian(ylim=c(0, .5))+  
  scale_y_continuous(breaks=seq(0, 0.5, .1)) +
  scale_fill_manual(name="Region", # Legend label, use darker colors
                    # breaks=c("1", "2", "3"),
                    breaks=c("0", "1"), 
                    labels=c("Ingushetia", 
                             "Chechnya"),
                    values=c("gray88", "grey44")) +
  theme(text = element_text(size=10),
        axis.line = element_line(colour = "black"),
        axis.title.x = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank())
figure6
```

\pagebreak
# References
