---
title: "Replication"
author: "Daniel Shapiro"
date: "2/16/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(readr)
```

```{r}
w <- read.csv2("wp_data_Chechnya_Ingushetia.csv")
x <- read.csv2("wp_data_courts.csv")
y <- read.csv2("wp_data_raw.csv")
z <- read.csv2("wp_data_survey.csv")
```

```{r}
summary(y)
```

NOTE: I think that I'm going to change my paper. The last paper that I had was entirely in Stata and given that I do not know Stata, I don't relish replicating that. The title of this paper is: "Laws in Conflict: Legacies of War, Gender, and Legal Pluralism in Chechnya." The data here is much cleaner -- mainly, it's in R; plus, I know Egor Lazarev (the author) and have talked with him in the past; I wrote my thesis on a similar topic and he and I interacted when he was visiting the Davis Center. I already have all of his contact info and I think it would be neat to work on this paper.

Link to github repo: https://github.com/dfshapir/Replication